Leadership across cultures and contexts: an exploratory analysis

### 2020-04-21 leadership_across_cultures_contexts.Rmd
Added random effects. Not filtering out rows with all 0's. Keeping any variable with at least 1 row with evidence.

```{r FunctionRE, fig.cap="Ethnographer and Culture random effects for function variables."}
# plot_fun_auth_cult_re
```

```{r QualityRE, fig.height=8, fig.cap="Ethnographer and Culture random effects for quality variables."}
# plot_qual_auth_cult_re
```

>>>>

```{r FunctionRE, fig.cap="Ethnographer and Culture random effects for function variables."}
plot_fun_auth_cult_re
```

```{r QualityRE, fig.height=8, fig.cap="Ethnographer and Culture random effects for quality variables."}
plot_qual_auth_cult_re
```
